---
output:
  md_document:
    variant: markdown_github
---

[![Travis-CI Build Status](https://travis-ci.org/jjesusfilho/stfstj.svg?branch=master)](https://travis-ci.org/jjesusfilho/stfstj)

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# stfstj

The goal of stfstj is to download data from the Brazilian Supreme Court decisions 

## Installation

You can install stfstj from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("jjesusfilho/stfstj")
```

You also have to make sure the packages [tesseract](https://github.com/ropensci/tesseract) and [pdftools](https://github.com/ropensci/pdftools) are installed also their dependencies.

## Usage

Suppose you want to download the metadata lawsuits precedentes (acordãos) with the expression "excesso de prazo". You can run this function:

```{r example1,eval=FALSE}
df<-stf_metadata(open_search="excesso de prazo",database="acordaos")
```

Or simply:

```{r example2,eval=FALSE}
df<-stf_metadata("excesso adj2 prazo")
```

Using "adj2" you are telling the engine that "prazo" is one word apart from "excesso". You don't have to include "acordaos" in the argument `database` because this is the default.

I you want to search for monocratic decisions, you specify it in the `database` argument:

```{r example3,eval=FALSE}
df<-stf_metadata("excesso adj2 prazo",database="monocraticas")
```

In order to find all the options, use the help function:

```{r example4,eval=FALSE}
?stf_metadata()
```


